Verifying Demonstrations

### 2020-02-25 paper/DB-Schnorr-UWB.tex
Renames DB-anon-cred to DB-Schnorr-UWB
Retitles DB-Schnorr-UWB to "UWB DB Schnorr protocol"
Comments out Tamarin spec
Improves UWB-MF proof (#9)

\section{Distance-bounding \aclp*{ZKPK} for discrete logarithms}%
\label{DB-anon-cred}

@@

\subsection{\Acl*{ZK} and \acl*{PK}}

@@

\daniel{Still intuition, we need to use the formal definition of security 
  above.}
\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \left(\frac{1}{m}+\frac{1}{q}\right)^n\), 
  where \(m, q\) are as in \cref{DB-Schnorr}.
\end{theorem}

\begin{proof}
  The adversary has two options:
  \begin{enumerate*}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, this yields success with probability 
    \(\frac{1}{m}\);
  \item guess the response, this yields success with probability 
    \(\frac{1}{q}\).
  \end{enumerate*}
  The total success probability is \(\frac{1}{m} + \frac{1}{q}\) per round, 
  thus \(\left(\frac{1}{m}+\frac{1}{q}\right)^n\) in total per protocol 
  session.
\end{proof}

>>>>

\section{Distance-bounding \aclp*{ZKPK} for discrete logarithms}%
\label{DB-Schnorr-UWB}

@@

\subsection{\Acl*{ZK} and \acl*{PK}}\label{UWB-ZKPK}

@@

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \left(\frac{1}{m}+\frac{1}{q}\right)^n\), 
  where \(m, q\) are as in \cref{DB-Schnorr}.
\end{theorem}

\begin{proof}
  It follows from the \ac{ZK} property (\cref{UWB-ZKPK}) that the adversary 
  cannot learn anything by observation.
  This leaves the adversary with two options:
  \begin{enumerate*}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, receiving the challenge first would taint the 
    session (\cref{TaintedMF});
  \item guess the response.
  \end{enumerate*}
  The first option yields success with probability \(\frac{1}{m}\), since the 
  choice is uniformly distributed.
  The second option yields success with probability \(\frac{1}{q}\): since the 
  response~\(s_i\) depends on \(\rho\), which is uniformly distributed in 
  \(\ZZ_q\), it follows that \(s_i\) is also uniformly distributed in 
  \(\ZZ_q\).

  The total success probability is \(\frac{1}{m} + \frac{1}{q}\) per round, 
  thus \(\left(\frac{1}{m}+\frac{1}{q}\right)^n\) in total per protocol 
  session.
\end{proof}
